ASYMPTOTIC VALIDITY OF THE BAYES-INSPIRED INDIFFERENCE ZONE PROCEDURE:

### 2015-05-07 paper/wish/wsc15paper.tex
Finishing compilation after getting all images.

We now use simulation experiments to illustrate and further investigate the phenomenon characterized by Theorem~\ref{t:main}. Using the version of BIZ described in Section~\ref{sec:BIZ} with maximum elimination ($c=1-(P^*)^\frac{1}{k-1}$), we estimate and then plot the PCS as a function of $\delta$ using 10,000 independent replications. We consider three different examples, setting $P^*=0.9$ in all three.

Our first example, illustrated in Figure~\ref{fig: tahi3}, is a known variance slippage configuration. Specifically, we consider $100$ systems with independent normally distributed samples, where $\mu_{k}=\delta,\mu_{k-1}=0,\dots,\mu_{1}=0$, $\delta$ is within the interval $[0.1,10]$, and $\lambda_{100}=1,\lambda_{99}=1+\frac{(0.5)(98)}{99},\cdots,\lambda_{1}=0.5$. Here, $n_{0}=0$. Figure ~\ref{fig: tahi3} shows that in this example the IZ guarantee is always satisfied, and the PCS approaches $P^*$ as $\delta$ goes to zero. When $\delta$ is big enough, the PCS is almost one because the difference between the best system and the others is large enough to be easily identifiable by the BIZ procedure. Here, the points plotted have central confidence intervals of length at most $0.014$.

\begin{figure}[h]
  \centering
   \begin{subfigure}[b]{0.3\textwidth}
      \centering
       \includegraphics[width=\textwidth]{plot5}
    \caption{
    \label{fig: tahi3}}
   \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
         \includegraphics[width=\textwidth]{plot3}
             \caption{
    \label{fig: tahi2}}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
         \includegraphics[width=\textwidth]{plot1}
    \caption{ \label{fig: tahi}}
    \end{subfigure}
    \caption{(a)  Known variances and $P^*=0.9$. In this example, our theorem is true: the IZ guarantee is always satisfied and the inequality is tight as $\delta$ goes to zero. (b) Unknown variances and $P^*=0.9$. In this example, our theorem is true: the IZ guarantee is satisfied and the inequality is tight as delta goes to zero. If we want that the IZ guarantee be satisfied in all the cases, we can just increment $n_{0}$. (c) Known variances, $P^*=0.9$ This was a hard example to find and it was specially chosen to illustrate our theorem. In practice, we would choose $n_{0}>0$ and the IZ guarantee will be satisfied.
\label{fig:tahi10}}
\end{figure}

@@

We should note that
this is a difficult example, and still we have a good performance in most of the cases. However, if we want to always satisfy the IZ guarantee, 
we can just increment the parameter $n_{0}$. Here, the points plotted have central confidence intervals of length at most $0.014$.

Now, we consider a pathological case when the variances are known. Specifically, we consider a slippage configuration 
with $100$ systems normally distributed, where $\mu_{100}=\delta,\mu_{99}=0,\dots,\mu_{1}=0$, $\delta$ is 
within the interval $[0.1,10]$, and $\lambda_{100}=10,\lambda_{99}=\cdots=\lambda_{1}=1$. Here, $P^*=0.9$ and $n_{0}=0$.
This configurations was specially chosen to illustrate our theorem, and so it is harder than typical configurations.
In fact, in most of the configurations the algorithm always satisfies the IZ guarantee. Furthermore, in practice, we would
have run the algorithm with $n_{0}>0$, and the BIZ algorithm would have worked well even in this pathological example. 
Figure ~\ref{fig: tahi} shows that PCS converges to $0.9$ as $\delta$ goes to zero. Specifically, PCS is equal to $0.904$ when $\delta=0.1$.
This figure also shows that the bound is tight  on probability of correct selection. We should also note that the number of samples required increases very fast. Here, the points plotted have central confidence intervals of length at most $0.014$.

>>>>

We now use simulation experiments to illustrate and further investigate the phenomenon characterized by Theorem~\ref{t:main}. Using the version of BIZ described in Section~\ref{sec:BIZ} with maximum elimination ($c=1-(P^*)^\frac{1}{k-1}$), we estimate and then plot the PCS as a function of $\delta$.
In all examples, $P^*=0.9$, PCS was estimated using 10,000 independent replications, and confidence intervals have length at most $0.014$.

Our first example, illustrated in Figure~\ref{fig: tahi3}, is a known variance slippage configuration. Specifically, we consider $100$ systems with independent normally distributed samples, where $\mu_{k}=\delta,\mu_{k-1}=0,\dots,\mu_{1}=0$, $\delta$ is within the interval $[0.1,10]$, and $\lambda_{100}=1,\lambda_{99}=1+\frac{(0.5)(98)}{99},\cdots,\lambda_{1}=0.5$. Here, $n_{0}=0$. Figure ~\ref{fig: tahi3} shows that in this example the IZ guarantee is always satisfied, and the PCS approaches $P^*$ as $\delta$ goes to zero. When $\delta$ is big enough, the PCS is almost one because the difference between the best system and the others is large enough to be easily identifiable by the BIZ procedure.

\begin{figure}[h]
  \centering
   \begin{subfigure}[b]{0.3\textwidth}
      \centering
       \includegraphics[width=\textwidth]{plot5.pdf}
    \caption{
    \label{fig: tahi3}}
   \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
         \includegraphics[width=\textwidth]{unknown.pdf}
             \caption{
    \label{fig: tahi2}}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
         \includegraphics[width=\textwidth]{plot3.pdf}
    \caption{ \label{fig: tahi}}
    \end{subfigure}
    \caption{(a)  Known variances and $P^*=0.9$. In this example, our theorem is true: the IZ guarantee is always satisfied and the inequality is tight as $\delta$ goes to zero. (b) Unknown variances and $P^*=0.9$. In this example, our theorem is true: the IZ guarantee is satisfied and the inequality is tight as delta goes to zero. If we want that the IZ guarantee be satisfied in all the cases, we can just increment $n_{0}$. (c) Known variances, $P^*=0.9$ This was a hard example to find and it was specially chosen to illustrate our theorem. In practice, we would choose $n_{0}>0$ and the IZ guarantee will be satisfied.
\label{fig:tahi10}}
\end{figure}

@@

We should note that
this is a difficult example, and still we have a good performance in most of the cases. However, if we want to always satisfy the IZ guarantee, 
we can just increment the parameter $n_{0}$.

Now, we consider a pathological case when the variances are known. Specifically, we consider a slippage configuration 
with $100$ systems normally distributed, where $\mu_{100}=\delta,\mu_{99}=0,\dots,\mu_{1}=0$, $\delta$ is 
within the interval $[0.1,10]$, and $\lambda_{100}=10,\lambda_{99}=\cdots=\lambda_{1}=1$. Here, $P^*=0.9$ and $n_{0}=0$.
This configurations was specially chosen to illustrate our theorem, and so it is harder than typical configurations.
In fact, in most of the configurations the algorithm always satisfies the IZ guarantee. Furthermore, in practice, we would
have run the algorithm with $n_{0}>0$, and the BIZ algorithm would have worked well even in this pathological example. 
Figure ~\ref{fig: tahi} shows that PCS converges to $0.9$ as $\delta$ goes to zero. Specifically, PCS is equal to $0.904$ when $\delta=0.1$.
This figure also shows that the bound is tight  on probability of correct selection. We should also note that the number of samples required increases very fast.
